Human Factors Influencing Visual Statistical Inference

### 2013-06-07 sociology_paper.tex
figure placement changed
plot for demographic factor main effect added
subject-wise residual time taken

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=0.99\textwidth]{tower.pdf} 
   \caption{ \label{fig:tower} Which of these towers is the most extreme? Which side is higher?}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf} 
   \caption{Mean residuals of time taken obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt. Linear regression lines are fitted through the points. For all the experiments the significantly downward slopes indicate that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}

@@

>>>>

\begin{figure}[hbtp] 
   \centering
   \includegraphics[width=0.99\textwidth]{tower.pdf} 
   \caption{ \label{fig:tower} Which of these towers is the most extreme? Which side is higher?}
\end{figure}

@@

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf}    
   \includegraphics[width=6.5in]{learning_trend_time_subject.pdf}    
   \caption{ Mean residuals of log(time taken) obtained from model \eqref{eqn:trend_time} fitted without covariate attempt plotted against attempt (above).  Subject-wise residuals of log(time taken) vs attempt (below). Linear regression lines are fitted through the points. For all the experiments the significantly downward slopes indicate that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{demographic_effect.pdf} 
   \caption{Boxplots of average time taken in log scale and proportion correct responses of all the lineups plotted for each demographic factor variables. None of the demographic factors appear to be statistically significant except India effect for proportion correct. Effect of graduate degree in proportion correct is also significant but is actually the India effect since, Most of the graduate degree holders are coming from India.}
   \label{fig:gender_country}
\end{figure}
